### 2020-03-14 paper/main.tex
updated intro

@@

As time series datasets become ever so popular the need for deep learning models becomes greater.
In our black-box model, we analyze deep learning models such as CNN’s which have become increasingly popular and widely used in the last decade but their complex nature makes it difficult for users to understand what is going on \cite{wang_hybrid_2019}. So, as black-box models get more popular the need for an interpretable accessory is needed so we propose a hybrid model consisting of a black box for classification and an interpretable white-box model which highlights characteristics of a time series for users to understand.

@@

We take advantage of wavelets by applying discrete wavelet transforms as a filter-bank, which means it is composed of cascading high-pass and low-pass filters. This gives us the advantage of splitting a signal into several frequency sub-bands. Wavelet decompositions give us the advantage of gaining features that take into account frequency and time domains.

>>>>

In this thesis, we study interpretable machine learning as applied to complex-valued time-series data. Scientists have studied the use of several machine learning methods such as Convolutional Neural Networks, Recurrent Neural Networks, and Support Vector Machines for time series classification. These methods, however, fall short of allowing users to visualize patterns within their dataset.

To address this issue, we propose an interpretable hybrid model that can be extended to any time series dataset. In the majority of existing work in the field of interpretability, black-box models tend to outperform white-box models consistently. However, instead of relying purely on one method, we propose a collaboration between the two. This gives us the performance of a black-box while allowing us to visualize features of the majority of our dataset.

To accomplish this, we created a framework composed of two models, an ensemble method of classifiers that functions as a black-box method, and a white-box model that encodes time series as images. The white-box model attempts to classify them through a neural network and outputs all images correctly classified in both black-box and white-box models.

@@

As time series datasets become ever so popular the need for deep learning models becomes greater.
In our black-box model, we analyze deep learning models such as Convolutional Neural Networks which have become increasingly popular and widely used in the last decade but their complex nature makes it difficult for users to understand what is going on inside \cite{wang_hybrid_2019}. So, as black-box models get more popular and increase in complexity the need for an interpretable accessory is needed so we propose a hybrid model consisting of a black-box for classification and an interpretable white-box model which highlights characteristics of a time series for users to understand.

The goal of our work is not to find an alternative to black-box methods but to provide a way for users to have an understanding of what features are prevalent in their dataset.

@@

We take advantage of wavelets by applying discrete wavelet transforms as a filter-bank, which means it is composed of cascading high-pass and low-pass filters. This allows us to split a signal into several frequency sub-bands. We focus on wavelet decomposition as our feature extractor because it outperformed all other methods in terms of accuracy and training time.
